\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{indentfirst}

\author{Adrien Matricon}

\setlength{\parskip}{1em}

\begin{document}

\title{Battle For Eden Rulebook}
\maketitle


    Civilizations rise and fall across the multiverse.

    Meanwhile, a place is left untouched, never knowing magic or technology.
    Its peaceful fairy inhabitants live in harmony with nature,
    never knowing hunger or lacking anything, for it is a land of abundance.
    A land filled with all kinds of riches, a land filled with all kinds of resources,
    and above all a land filled with rare energy crystals: a land called Eden!

    When energy crystals become so numerous that portals to Eden suddendly open
    throughout the multiverse, it is time for civilizations to go to war!
    War for crystals! War for resources! This is the battle for Eden!



\section{Introduction}

    Battle For Eden is a war game involving conquest, resource production and deck
    building.
    Each player embodies a different civilization, and as such uses different cards and
    relies on different resources than other players, giving birth to an asymetric game
    with a lot of replayability!

    As civilizations discover Eden, they may face various situations.
    This game comes with various scenarios, each with its own victory conditions.
    Some scenarios will pitch players against one another, while other will have
    them cooperate to survive!
    Whichever scenario you choose, fight for the prosperity of your civilization!


\newpage
\section{Contents}

    \begin{itemize}
        \item This rulebook
        \item Civilization unit cards
            \begin{itemize}
                \item 8 cost-1 unit cards
                \item 6 cost-2 unit cards
                \item 4x4 cost-3 unit cards
                \item 3 cost-5 unit cards
                \item 2 cost-6 unit cards (immortal unit cards)
            \end{itemize}
        \item Common cards
            \begin{itemize}
                \item Energy Crystal cards
                    \begin{itemize}
                        \item 30 Small Energy Crystal cards
                        \item 20 Medium Energy Crystal cards
                        \item 20 Huge Energy Crystal cards
                    \end{itemize}
                \item Tactical cards
                    \begin{itemize}
                        \item 20 Setback cards
                        \item 20 Opportunity cards
                    \end{itemize}
            \end{itemize}
        \item Territoriy tiles
            \begin{itemize}
                \item 1 Heart of Eden tile
                \item 6 Portal tiles (1 for each civilization)
                \item 74 normal tiles
            \end{itemize}
        \item Occupation tokens
        \item Resource tokens
        \item Material for the King of Eden scenario
            \begin{itemize}
                \item 1 King of Eden figurine
                \item 1 20-faced dice
                \item an attack deck
            \end{itemize}
    \end{itemize}


\newpage
\section{Setup}

    \begin{description}
        \item[Civilization choice] \hfill \\
            Each player chooses a civilization, and takes the corresponing
            \textbf{portal tile} as well as \textbf{occupation tokens}.
            He then takes all \textbf{unit cards} of that civilization and puts them
            in front of him as a pile, face up.
            This pile is called his \textit{\textbf{World}}.
        \item[Common cards] \hfill \\
            Create \textbf{a pile of each type of common card},
            and place them somewhere where every player can access them.
        \item[Deck creation] \hfill \\
            Each player takes \textbf{5 Small Energy Crystal cards}
            from the corresponding pile and \textbf{3 cost-1 units cards} from his World,
            then \textbf{shuffle them} to create his deck.
        \item[Other] \hfill \\
            The last player to have lost a game (of any kind) is the first player.
            By the way, you just lost the game. You know, \textit{the game}.
    \end{description}


\section{Some definitions}

    \begin{description}
        \item[Distance between two tiles] \hfill \\
            The number of frontiers one needs to cross to go from one tile to the another.
            For example, the distance between two tiles in contact is 1.
        \item[Discard pile] \hfill \\
            A pile of face-up cards (empty at the begging) besides a player's deck.
            Any player may look into any other player's discard pile.
            No player is allowed to change the order of the cards in any discard pile.
        \item[Discarding a card] \hfill \\
            Putting a card on top of its owner's discard pile.
        \item[Spending resources] \hfill \\
            Removing a given number of resource tokens from one's territories.
        \item[Spending Energy Crystals] \hfill \\
            Discarding Energy Crystal cards whose total value is at least a given number.
        \item[Buying a card] \hfill \\
            Paying a cost to add a card to one's discard pile.
        \item[Destroying a card] \hfill \\
            Putting a card in the pile where it can be bought back.
            Destroyed common cards go into the corresponding piles,
            while destroyed unit cards go back to their World.
    \end{description}


\newpage
\section{Map creation phase}

    The first phase of the game is the creation of the map.
    
    For each player, take out one tile of each color from the game box.
    Then add to those yet another tile of each color, shuffle all those tiles together,
    and place them on the table face down as a pile.
    Place the Heart of Eden tile at the center of the table.
    
    Then, starting with the first player, all players take turns building the map.
    Each turn starts by revealing the top tile of the pile and placing it on the map.
    A tile may be placed anywhere next to the Heart of Eden tile or to another normal
    tile, as long as it leaves the map in a \textbf{valid state} (see below).
    In cooperative game modes (or for a quick start), each tile is placed first,
    then revealed.
    
    At any time during his turn, a player is allowed to place his Portal tile
    next to normal tiles.
    It can be placed anywhere, as long as it is in contact with either two tiles
    (normal case), or three tiles (in which case, he removes one of those and shuffles
    it back into the tile pile), and that it leaves the map in a \textbf{valid state}
    (see below).
    A player that has already placed his Portal tile may also remove it from the map at
    any time during his turn.    
    
    A \textbf{\textit{valid state}} of the map is one in which:
    \vspace{-1.3em}
    \begin{itemize}
        \item Every Portal tile is in contact with exactly 2 tiles,
        \item The distance between any 2 Portal tiles is 4 or more,
        \item The distance between any Portal tile and the Heart of Eden tile
        is 4 or more.
    \end{itemize}
    
    \vspace{-0.7em}
    If there is no tile left in the pile, a player's Portal tile has to be part of the
    map at the end of his turn.
    If it cannot be placed, he instead removes on normal tile from the map, puts it on
    top of the empty tile pile, and ends his turn.
    
    The map creation phase ends when the tile pile stays empty long enough for each
    player to take 2 turns.


\newpage
\section{Main phase}

  \subsection{Beginning}
  
  	\begin{itemize}
        \item Place 1 resource token of each type on the Heart of Eden.
        \item Players take control of the territories in contact with their Portal
        territory, and materialize it by putting Occupation tokens on them.
        \item Players may \textbf{manage their territories} (see below).
        \item Player draw 5 cards from their decks to constitute their starting hands.
    \end{itemize}


  \subsection{A player's turn}

    \hspace{-1.5em} During his turn, a player can perform several actions,
    which can be done in any order but not simultaneously:
    \vspace{-1.3em}
    \begin{itemize}
        \item Discarding any card from his hand (any number of times)
        \item Buying cards (any number of times)
        \item Managing his territories (only once per turn)
        \item Launching attacks on territories (only once per turn)
        \item Making a breakthrough (only after successfully conquering territories)
    \end{itemize}
    
    \vspace{-0.7em}
    At the end of a player's turn, \textbf{any player} whose hand contain less than 5
    cards \textbf{can replenish his hand to 5 cards}.


  \subsection{Drawing and discarding cards}
    
    During his turn, a player may choose discarding card as an action.
    In this case, he may discard any number of cards from his hand.

    When a player must draw more cards from his deck
    (whether to replenish his hand or because of a card's effect)
    or reveal more cards from the top of his deck than his deck contains cards,
    that player must replenish his deck before drawing or revealing the cards.
    To do so, he shuffles his discard pile and puts the cards under his deck.


\newpage
  \subsection{Resources}
  
    Territories may hold any number of resources (there is no upper limit),
    materialized by resource tokens. Those resources can be of 7 types:
    
    \vspace{-1.3em}
    \begin{itemize}
        \item Shards (white tokens)
        \item Plants (green tokens)
        \item Animals (red tokens)
        \item Ores (grey tokens)
        \item Gems (violet tokens)
        \item Rare Elements (yellow tokens)
        \item Inhabitants (pink tokens)
    \end{itemize}
    
    \vspace{-0.7em}
    A player's Occupation tokens are used to materialize which territories he controls.
    Controlling a territory allows the player to spend the resources it holds,
    as well as to produce or destroy those resources during territory management.
  
  
  \subsection{Buying cards}

    During his turn, a player may choose to buy cards.
    He may buy Energy Crystal cards (in-universe: refining shards),
    buy Tactical cards (in-universe: making use of the terrain)
    or buy Unit cards (in-universe: asking for reinforcement).
    
    \hspace{-1.5em} \textbf{IMPORTANT:
    A player can only ask for reinforcements if his Portal territory was not destroyed.
    }
    
    Buying cards first implies paying a cost, by spending resources and Energy Crystals
    (or only resources in the case of common cards).
    Once the cost has been paid, the card is put on top of the player's discard pile.
    
    \hspace{-1.5em} \textbf{IMPORTANT:
    Each civilization relies heavily on one type of resource, or
    \textit{valuable resource} (see the color of the cubes on their unit cards).
    As such, the only resources a player can spend are Shards and his civilization's
    valuable resource.
    }


\newpage
  \subsection{Managing one's territory}
  
    Each territory has a given \textit{production capacity} for each type of resource.
    The production capacity of a normal territory in the resource of their color is 2.
    
    Besides that, the production capacity of a territory in any type of resource
    is 1 by default.
    In particular, Portal territories are considered to have a production capacity
    of 1 in every type of resource.
    If a unit card is played on a tile on the border of the map and mentions the
    production capacity of the neighbouring tiles, the "missing" tiles are also
    considered to have a production capacity of 1 in every type of resource.
    
    \hspace{-1.5em}Once per turn, a player can manage the territories he controls:
    \vspace{-1.3em}
    \begin{description}
        \item[Normal territory] \hfill \\
        	For each normal territory, he may choose to either:
            \vspace{-0.7em}
            \begin{itemize}
        		\item produce: he chooses a type of resource and then puts
            	on this territory as many new resource tokens of that type that its
            	production capacity for that resource,
        		\item destroy resources: he removes half of the resource
            tokens of each type of resource on this territory (rounded up),
        		\item do nothing.
    		\end{itemize}
        \item[Heart of Eden] \hfill \\
        	For the Heart of Eden, he may choose to either:
            \vspace{-0.7em}
            \begin{itemize}
        		\item produce: add one resource of each kind of the Heart of Eden,
        		\item do nothing.
    		\end{itemize}
        \item[Portal territory] \hfill \\
        	Nothing to do here.
    \end{description}


\subsection{Launching an attack}

    Once per turn, a player may choose frontiers between territories he controls and other
    territories and start a battle on each of those frontiers.
    Each of those battles takes place on a separate "front"
    (see next section for more information on combat).

    Once combat is over, if the attacking player won battles on some fronts,
    he takes control of the corresponding territories by removing the Occupation tokens of
    the previous controller of the conquered territories (if any) and putting his own
    Occupation tokens on it.
    At that time, he may move resources as he wishes between the two territories on each
    side of the victorious fronts.
    
    \hspace{-1.5em} \textbf{
    IMPORTANT: winning on one front is enough to take control of a territory.
    }

    If the conquered territory was a Portal territory, the tile is instead destroyed
    (i.e. removed from the map).


\subsection{Making a breakthrough}

    If at least one territory controlled by other players was conquered during his attack
    phase, the attacking player earns the right to perform a breakthrough.

    \hspace{-1.5em} To make a breakthrough, the player:
    \vspace{-1.3em}
    \begin{enumerate}
        \item replenishes his hand to 5 cards,
        \item selects any number of frontiers on his new territories (possibly none),
        \item launches an attack on the selected frontiers,
        \item discards all cards in his hand.
    \end{enumerate}
    
    \vspace{-0.7em}
    \hspace{-1.5em} \textbf{
    IMPORTANT: If the player conquered territories controlled by other players in step 3,
    he may choose to perform a second
    (and last) breakthrough from his newly conquerred territories instead of going to
    step 4.
    }
    
    \hspace{-1.5em} \textbf{
    IMPORTANT: When a player's territories are attacked during a breaktrough,
    he may immediately discard any number of cards from his hand then replenish
    it to 5 cards.
    }


\section{Combat}

  \subsection{Attacking a single player-controlled territory}
  
    \hspace{-1.5em} In the case where there is a single front,
    against a player-controlled territory:
    \vspace{-1.3em}
    \begin{enumerate}
        \item The attacking player plays a unit card from his hand on the front,
        hereby launching the attack,
        \item If he has not stopped defending,
        the defending player may either play a unit on this front or stop defending,
        \item If he has not stopped attacking,
        the attacking player may either play a unit on this front or stop attacking,
        \item Repeat step 2 and 3 until both player have stopped attacking or defending,
        \item On each side, sum the strengths of all units,
        The attacking player wins the battle on this front if the total strength
        of his units is strictly more than that of the defending player's,
        \item Post-combat phase (see below).
        \item Unit-destruction phase (see below)
    \end{enumerate}
    

  \subsection{Attacking multiple player-controlled territory}
    
    The battle on each front is similar to what is described above,
    but each battle take place in parallel:
    each step has to be performed on each front before going to the next step.
    

  \subsection{Attacking wild territories}
    
    \textbf{\textit{Wild territories}} are territories that are not controlled by any
    player.
    
    When wild territories are among the attacked territories,
    everything happens on the corresponding fronts as if there was a defending player
    who stopped defending in step 2.
    
    When step 5 is reached, the battle is won by the attacking player if the total
    strength of his units is at least equal to the distance of the wild territory
    to the closest Portal territory.


\subsection{Effects and abilities}

    Cards played during combat don't simply add strength to their side.
    They also have effects and abilities that greatly impact how the battle unfolds.
    A distinction must be done between permanent effects and triggered abilities.

    \begin{description}
        \item[Permanent effects] \hfill \\
        	Those are additional rules that apply to a card,
            like special buying conditions, ways to use it from your hand, 
            increased force in battle under certain conditions for a unit, etc.
        \item[Triggered abilities] \hfill \\
            Units in battle allow their owner to trigger their abilities at
            specific times, which are events that can have varying effects.
            A player can always choose whether to trigger an ability or not.
            
            Triggered abilities may be of 4 types,
            depending on when they can be triggered:
            \begin{description}
        	        \item[Immediate abilities]
                    	may be triggered just after the unit is added to the battle.
        	        \item[Delayed abilities]
                    may be triggered when all players stopped attacking/defending,
	                before the actual end of the battle.
        	        \item[Reaction abilities] may be event-based or condition-based.
	            \begin{description}
                        \item[Event-based:]
                        they may be triggered each time a specific event occurs
                        (example of event: "collapse of this unit").
                        \item[Condition-based:]
                        they may be triggered each time the event
                        "the card is played while the condition is satisfied" or the
                        event "the condition just became satisfied" occurs.
                        (example of condition: "no card in your hand").
                    \end{description}
        	        \item[Post-combat abilities] may be triggered at the beggining of the
                    post-combat phase, before doomed units are destroyed.
            \end{description}
    \end{description}
    
    If several abilities can be triggered at the same time,
    they may all be triggered successively.
    The order in which they are triggered is decided by the player that triggers them.
    If several players want to trigger an ability at the same time,
    the attacking player may trigger his first,
    then the priority goes to the player that plays after him, and so on.
    

  \subsection{Collapse, doom, unit destruction phase and post-combat phase}
  
    Some units'abilities allow them to \textbf{\textit{get rid of}} another unit.
    Units targetted by those abilities \textbf{\textit{collapse}},
    which means they are removed from the battle and put aside into a pile
    of \textbf{\textit{collapsed units}} until the post-combat phase.
    
    Similarly, units may be \textbf{\textit{doomed}} during the battle.
    The dooming of a unit is materialized by turning it horizontally to the right.
    Doomed units collapse during the post-combat phase.

    Some abilities allow to \textbf{\textit{save}} a doomed unit,
    meaning it becomes undoomed again.
    Please note that a doomed unit cannot be doomed again,
    and that an undoomed unit cannot be saved.
    
    During the post-combat phase, doomed units collapse,
    then all units that remain in battle are discarded by
    their owners in any order.
    
    During the unit-destruction phase, \textbf{collapsed immortal units
    (i.e. cost-6 units) are first discarded}.
    Then, each player may choose up to one of his collapsed units to
    \textbf{\textit{rescue}}.
    To do so, the player spends as many valuable resources as this unit's cost.
    Rescued units are discarded while all other collapsed units are destroyed.
    
    
    



\end{document}

